Indexes measures for oak decline severity using phenotypic descriptors

### 2019-08-28 manuscript/figures.Rmd
added site location map figure

```{r library_load}
source('../code/library_load.R')
```

@@

>>>>

```{r library_load,cache=FALSE}
source('../code/library_load.R')
```

@@

```{r siteLocations,fig.cap='Map showing locations of the nine sites used for collection of phenotypic descriptors.',fig.width=3,fig.height=5}
source('../code/site_locations.R')
site_locations_map
```
